### 2016-09-11 draft/draft.tex
Update formatting

\begin{abstract}
 This is cool paper about vuvuzelas.
\end{abstract}

\renewcommand{\abstractname}{Acknowledgements}
\begin{abstract}
 Thanks Mum!
\end{abstract}

@@

\begin{figure}[htbp]
\centering
\includegraphics{../diagrams/educationalConditions.png}
\caption{A theory on educational conditions that promote intellectual
engagement}
\end{figure}

@@

\begin{figure}[htbp]
\centering
\includegraphics{../screenshots/socialx.png}
\caption{SocialX's reputation overview}
\end{figure}

@@

\begin{figure}[htbp]
\centering
\includegraphics{../screenshots/wikispaces.png}
\caption{The WikiSpaces Classroom dashboard}
\end{figure}

@@

\begin{figure}[htbp]
\centering
\includegraphics{../screenshots/haikulearning.jpg}
\caption{The HaikuLearning dashboard}
\end{figure}

@@

\begin{figure}[htbp]
\centering
\includegraphics{../diagrams/conceptDiagram.png}
\caption{An early conceptual diagram demonstrating possible interactions
with the system}
\end{figure}

@@

\begin{figure}[htbp]
\centering
\includegraphics{../diagrams/simplifiedContractsClassDiagram.png}
\caption{A simplified class diagram to illustrate the relationships
between Factory, Manager and Linker contracts}
\end{figure}

@@

\begin{figure}[htbp]
\centering
\includegraphics{../diagrams/mvc.png}
\caption{A typical MVC Model\cite{1mvcfigure}}
\end{figure}

@@

\begin{verbatim}
// ...
if (isOverwrite) {
    return 0x0;
} else {
    User u = new User(_id, _username, _email, _name, _password);
    userList.insert(_username, u);
    return u;
}
// ...
\end{verbatim}

@@

\begin{verbatim}
contract UserManager {
    SequenceArray userList = new SequenceArray();

@@

    function isUsernameTaken(bytes32 _username) constant returns (bool) {
        registerActionEvent("IS USERNAME TAKEN");
        return userList.exists(_username);
    }
    // ...
}
\end{verbatim}

@@

\begin{verbatim}
app.post('/user/taken', function (req, res) {
    var username = req.body.username;

    log.info("POST /user/taken: ", username);
    userManager.isUsernameTaken(username, function (err, isTaken) {
        _handleErr(err, res);
        res.json({isTaken: isTaken});
    });
});
\end{verbatim}

@@

\begin{verbatim}
let STATUS_BAR_HEIGHT = Platform.OS === 'ios' ? 20 : 25;
let HEADER_HEIGHT = Platform.OS === 'ios' ? 44 + STATUS_BAR_HEIGHT : 56 + STATUS_BAR_HEIGHT;
\end{verbatim}

@@

\begin{verbatim}
describe("addTask", function () {
    it("adds the given task object to the chain and returns the registered task's hex address", function(done) {
        taskManager.addTask(testTask, function (error, address) {
            assert.isNull(error);
            assert.isString(address, "`address` should be the registered task's hex address");
            done();
        });
    });
});
\end{verbatim}

@@

\section{5.5 Coverage}\label{coverage}
Test coverage reports were generated automatically following each execution of the API's test suite. A coverage summary is shown below, while the full report can be located as browsable collection of HTML files in the repository's \texttt{chain/test/coverage} directory. Appendix E shows the index page of these HTML reports to provide an overview.

\begin{lstlisting}
  35 passing (45s)

=============================== Coverage summary ===============================
Statements   : 90.64% ( 426/470 ), 4 ignored
Branches     : 56.49% ( 74/131 ), 5 ignored
Functions    : 97.12% ( 135/139 ), 1 ignored
Lines        : 91.22% ( 426/467 )
================================================================================
\end{lstlisting}

>>>>

\begin{abstract}

\end{abstract}

\renewcommand{\abstractname}{Acknowledgements}
\begin{abstract}

\end{abstract}

@@

\begin{figure}[htbp]
\centering
\includegraphics[width=0.7\textwidth]{../diagrams/educationalConditions.png}
\caption{A theory on educational conditions that promote intellectual
engagement}
\end{figure}

@@

\begin{figure}[htbp]
\centering
\includegraphics[width=0.8\textwidth]{../screenshots/socialx.png}
\caption{SocialX's reputation overview}
\end{figure}

@@

\begin{figure}[htbp]
\centering
\includegraphics[width=0.8\textwidth]{../screenshots/wikispaces.png}
\caption{The WikiSpaces Classroom dashboard}
\end{figure}

@@

\begin{figure}[htbp]
\centering
\includegraphics[width=0.8\textwidth]{../screenshots/haikulearning.jpg}
\caption{The HaikuLearning dashboard}
\end{figure}

@@

\begin{figure}[htbp]
\centering
\includegraphics[width=0.7\textwidth]{../diagrams/conceptDiagram.png}
\caption{An early conceptual diagram demonstrating possible interactions
with the system}
\end{figure}

@@

\begin{figure}[htbp]
\centering
\includegraphics[width=0.9\textwidth]{../diagrams/simplifiedContractsClassDiagram.png}
\caption{A simplified class diagram to illustrate the relationships
between Factory, Manager and Linker contracts}
\end{figure}

@@

\begin{figure}[htbp]
\centering
\includegraphics[width=0.6\textwidth]{../diagrams/mvc.png}
\caption{A typical MVC Model\cite{1mvcfigure}}
\end{figure}

@@

\begin{lstlisting}
// ...
if (isOverwrite) {
    return 0x0;
} else {
    User u = new User(_id, _username, _email, _name, _password);
    userList.insert(_username, u);
    return u;
}
// ...
\end{lstlisting}

@@

\begin{lstlisting}
contract UserManager {
    SequenceArray userList = new SequenceArray();

@@

    function isUsernameTaken(bytes32 _username) constant returns (bool) {
        registerActionEvent("IS USERNAME TAKEN");
        return userList.exists(_username);
    }
    // ...
}
\end{lstlisting}}

@@

\begin{lstlisting}
app.post('/user/taken', function (req, res) {
    var username = req.body.username;

    log.info("POST /user/taken: ", username);
    userManager.isUsernameTaken(username, function (err, isTaken) {
        _handleErr(err, res);
        res.json({isTaken: isTaken});
    });
});
\end{lstlisting}

@@

\begin{lstlisting}
let STATUS_BAR_HEIGHT = Platform.OS === 'ios' ? 20 : 25;
let HEADER_HEIGHT = Platform.OS === 'ios'
    ? 44 + STATUS_BAR_HEIGHT
    : 56 + STATUS_BAR_HEIGHT;
\end{lstlisting}

@@

\begin{lstlisting}
describe("addTask", function () {
    it("adds the given task object to the chain and returns the registered task's hex address", function(done) {
        taskManager.addTask(testTask, function (error, address) {
            assert.isNull(error);
            assert.isString(address, "`address` should be the registered task's hex address");
            done();
        });
    });
});
\end{lstlisting}

@@

\section{5.5 Coverage}\label{coverage}
Test coverage reports were generated automatically following each execution of the API's test suite. A coverage summary is shown below, while the full report can be located as browsable collection of HTML files in the repository's \texttt{chain/test/coverage} directory. Appendix E contains extracts from the report.

\begin{lstlisting}
  35 passing (46s)

=============================== Coverage summary ===============================
Statements   : 91.28% ( 429/470 ), 7 ignored
Branches     : 58.02% ( 76/131 ), 7 ignored
Functions    : 98.56% ( 137/139 ), 3 ignored
Lines        : 91.86% ( 429/467 )
================================================================================
\end{lstlisting}
